Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Add a comment
initial abstruct.

TBD: Asbtract will be written at the final moment.

State the problem.

Say why it’s an interesting problem.

Say what your solution achieves.

Say what follows from your solution.

@@

>>>>

Many Haskell programmers tend not to write test code even though the
strong type system of Haskell cannot ensure correct semantics.
Without test code, it is difficult for users to understand usage of
functions and it is difficult for developers to maintain semantics
while progressing software. To motivate Haskell programmers to write
test code, we propose to carry out behavior driven development with
two tools: doctest integrated with QuickCheck for user documentation
and Hspec with combinators extended for developer documentation. With
our method, specification can be used for documentation and automatic
testing.

%% State the problem.
%% Say why it's an interesting problem.
%% Say what your solution achieves.
%% Say what follows from your solution.

@@

\begin{quote}\begin{itemize}
    \item sol: Should we state that BDD-style TDD has been pioneered
        by RSpec?
\end{itemize}\end{quote}
